XXX

### 2012-03-25 paper/engNERwiki.tex
09->08.
Appendix removed.

% Eszter: ehhez a felső listához hivatkozzam Nothmant? A fele tőle jön, viszont mi máshogy csináltuk kicsit.
Our solution is similar to Nothman's \shortcite{Nothman:09}. Instead of a trie, however, we use a set, albeit with more alias types. We expect more precise tagging from our slightly more rigorous solution.

@@

\begin{itemize}
\item names of languages, nationalities, religions, poltical ideologies;
\item adjectives derived from a NE;
\item names of months, days, holidays;
\item names of special events and wars.
\end{itemize}

There is an other special case in Hungarian: opposite to English, the number of compund words is quite large in Hungarian, and NEs can also be subjects of compounding. In this case the common noun following the NE is joint with a hyphen, so they constitute one token. However, the joint common noun can modify the original sense of NE, depending on the semantics of the common noun. For example: in the compound \textit{SAP-szoftvercég} ['SAP software company'] the common noun does not change the labeling, but in the case of the compound \textit{WorldCom-botrány} ['WorldCom scandal'] the NE tag changes from ORG to O.

@@

% HEEEEELP!
\appendix
\section{DBpedia to ConLL Mapping}
\label{sec:appa}

\begin{table*}[ht]
\begin{center}
\begin{tabular}{llll}
\hline DBpedia & \bf CoNLL & \bf DBpedia & \bf CoNLL \\ \hline
Person & PER & Library & LOC \\
Place & LOC & MeanOfTransportation & MISC \\
Organization & ORG & PeriodicalLiterature & ORG \\
Organisation & ORG & ProgrammingLanguage & MISC \\
Award & MISC & Project & MISC \\
EthnicGroup & MISC & SportsLeague & MISC \\
Event & MISC & SportsTeamSeason & O \\
Holiday & MISC & Weapon & MISC \\
Ideology & MISC & Work & MISC \\
Language & MISC & & \\
\hline
\end{tabular}
\end{center}
\end{table*}

>>>>

% Eszter: ehhez a felső listához hivatkozzam Nothmant? A fele tőle jön, viszont mi máshogy csináltuk kicsit.
Our solution is similar to Nothman's \shortcite{Nothman:08}. Instead of a trie, however, we use a set, albeit with more alias types. We expect more precise tagging from our slightly more rigorous solution.

@@

\begin{itemize}
\item names of languages, nationalities, religions, political ideologies;
\item adjectives derived from a NE;
\item names of months, days, holidays;
\item names of special events and wars.
\end{itemize}

There is another special case in Hungarian: opposite to English, the number of compund words is quite large in Hungarian, and NEs can also be subjects of compounding. In this case the common noun following the NE is joint with a hyphen, so they constitute one token. However, the joint common noun can modify the original sense of NE, depending on the semantics of the common noun. For example: in the compound \textit{SAP-szoftvercég} ['SAP software company'] the common noun does not change the labeling, but in the case of the compound \textit{WorldCom-botrány} ['WorldCom scandal'] the NE tag changes from ORG to O.

@@

%\appendix
%\section{DBpedia to ConLL Mapping}
%\label{sec:appa}
%
%\begin{table*}[ht]
%\begin{center}
%\begin{tabular}{llll}
%\hline DBpedia & \bf CoNLL & \bf DBpedia & \bf CoNLL \\ \hline
%Person & PER & Library & LOC \\
%Place & LOC & MeanOfTransportation & MISC \\
%Organization & ORG & PeriodicalLiterature & ORG \\
%Organisation & ORG & ProgrammingLanguage & MISC \\
%Award & MISC & Project & MISC \\
%EthnicGroup & MISC & SportsLeague & MISC \\
%Event & MISC & SportsTeamSeason & O \\
%Holiday & MISC & Weapon & MISC \\
%Ideology & MISC & Work & MISC \\
%Language & MISC & & \\
%\hline
%\end{tabular}
%\end{center}
%\end{table*}
